### 2014-06-26 3/sar.tex
auto

\section{Original Heteroskedastic Model of SAR data}

@@

\begin{equation}
\label{eqn:SAR Unit Amplitude PDF}
\caption{eqn:SAR Unit Amplitude PDF}
pdf(A_1) = 2A_1 e^{ \left( A_1^2 \right) }
\end{equation}
\begin{equation}
  \label{eqn:SAR Unit Intensity PDF}
  \caption{eqn:SAR Unit Intensity PDF}
pdf(I_1) = e^{ \left( -I_1 \right) }
\end{equation}

@@

\begin{table}[!h]
\normalsize
\centering
\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(A_1) = \frac{ \sqrt{\pi}}{2}$ & $var(A_1) = \frac{(4-\pi)}{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ & $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline 
\end{tabular}
\caption{ Mean and Variance of Original SAR data }
\label{tbl:orginal_sar_avg_var}
\end{table}

@@

\section{The Effects of Heteroskedasticity in SAR Processing}%IVM: shortened to make it look nicer

@@

The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously. 
Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
While the statistical model within individual resolution cells is well established,
  it is only applicable to homogeneous areas.
Practical images, however, are heterogeneous.
Furthermore, it is precisely this spatial variation that is often of high interest.
%And while the statistical model within individual resolution cells is well established,
%  the applicability of these models, however, are restricted to homogeneous areas. 
%Practical images, nevertheless, are heterogeneous. 
%Crucially it is this spatial variation that is of high interest. 
%This fact gives rise to the question that seemed obvious:
  %how to call an analysis area heterogeneous and subsequently
%  what to do in the case of heterogeneity.

@@

Heteroskedasticity also poses numerous challenges in designing an efficient estimator. Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator in serious doubt. 
If the variance is known \textit{a priori}, it has been proven \cite{Aitken_1934_ProcsRoyalSocEdinburg}, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980, Kuan_1985_PAMI, Frost_PAMI_1982} do make use of weighted mean estimations. 
The problem, however, is that in SAR speckle filtering, variance is not known \textit{a priori}. 
And even though variance can be estimated from observable values, as the ambiguity circle goes, estimating the variance is as hard as estimating the underlying coefficient $\sigma$ itself.

@@

\section{The Homoskedastic Effect of Logarithmic Transformation}

@@

\begin{equation}
  \label{eqn:SAR Unit Log Amplitude PDF}
  \caption{eqn:SAR Unit Log Amplitude PDF}
pdf(L_{1}^{A}) = 2 \cdot 2^{\left( 2 L_{1}^{A} \right)}e^{-2^{\left( 2 L_{1}^{A} \right) }} 
\end{equation}
\begin{equation}
  \label{eqn:SAR Log Amplitude PDF}
  \caption{eqn:SAR Log Amplitude PDF}
pdf(L_A) = 2 \cdot 2^{\left( 2 L_A - 2 \log_2 \sigma \right)}e^{-2^{\left( 2 L_A - 2 \log_2 \sigma \right)}} 
\end{equation}
\begin{equation}
  \label{eqn:SAR Unit Log Intensity PDF}
  \caption{eqn:SAR Unit Log Intensity PDF}
pdf(L_{1}^{I}) = 2^{L_1^I} e^{-2^{L_1^I}}  
\end{equation}
\begin{equation}
  \label{eqn:SAR Log Intensity PDF}
  \caption{eqn:SAR Log Intensity PDF}
pdf(L_I) = 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
\end{equation}

@@

\begin{table}[h]
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = - \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = - \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}

\caption{ Mean and Variance of Log Transformed values: here the variance is no longer dependent on $\sigma$ }
\label{tbl:sar_log_domain_avg_var}
%\end{center}
\end{table}

@@

\section{Consistent Measures of Distance in the Log-Transformed Domain}

@@

\begin{table}[H]
\centering
\small
%awk -F"&" '{print $4}' tmp.0.txt | awk -F"(" '{print $1}'
\begin{tabular}{c|c|c|c|c|c}
No  & 70\%            &75\%             &80\%             &85\%             &90\%\\
\hline
2   &2.9024 (0.0252)  &3.7088 (0.0261)  &4.7960 (0.0327)  &6.3488 (0.0242)  &8.7974 (0.0370)\\
3   &3.4698 (0.0141)  &4.1308 (0.0177)  &4.9585 (0.0245)  &6.1176 (0.0136)  &7.9207 (0.0316)\\
4   &3.6505 (0.0225)  &4.2096 (0.0386)  &4.9392 (0.0347)  &5.9195 (0.0341)  &7.4209 (0.0162)\\
5   &3.7421 (0.0134)  &4.2513 (0.0165)  &4.8967 (0.0297)  &5.7729 (0.0170)  &7.0725 (0.0250)\\
6   &3.7850 (0.0149)  &4.2588 (0.0242)  &4.8611 (0.0160)  &5.6449 (0.0162)  &6.8062 (0.0282)\\
7   &3.8274 (0.0119)  &4.2686 (0.0102)  &4.8179 (0.0117)  &5.5447 (0.0114)  &6.6049 (0.0158)\\
8   &3.8468 (0.0110)  &4.2591 (0.0124)  &4.7747 (0.0176)  &5.4519 (0.0087)  &6.4370 (0.0085)\\
9   &3.8610 (0.0081)  &4.2503 (0.0125)  &4.7430 (0.0120)  &5.3688 (0.0085)  &6.2829 (0.0112)\\
10  &3.8663 (0.0089)  &4.2423 (0.0126)  &4.6967 (0.0102)  &5.3015 (0.0103)  &6.1574 (0.0116)\\
11  &3.8707 (0.0089)  &4.2284 (0.0109)  &4.6693 (0.0078)  &5.2387 (0.0111)  &6.0473 (0.0122)\\
12  &3.8763 (0.0063)  &4.2228 (0.0072)  &4.6370 (0.0139)  &5.1805 (0.0050)  &5.9502 (0.0044)\\
13  &3.8808 (0.0048)  &4.2089 (0.0083)  &4.6096 (0.0055)  &5.1315 (0.0092)  &5.8654 (0.0070)\\
14  &3.8761 (0.0048)  &4.1920 (0.0112)  &4.5816 (0.0069)  &5.0845 (0.0058)  &5.7870 (0.0106)\\
15  &3.8806 (0.0048)  &4.1901 (0.0063)  &4.5592 (0.0088)  &5.0372 (0.0076)  &5.7158 (0.0119)\\
16  &3.8774 (0.0032)  &4.1778 (0.0060)  &4.5397 (0.0049)  &4.9985 (0.0087)  &5.6483 (0.0083)\\
17  &3.8760 (0.0043)  &4.1682 (0.0035)  &4.5149 (0.0060)  &4.9652 (0.0051)  &5.5919 (0.0078)\\
18  &3.8708 (0.0083)  &4.1584 (0.0026)  &4.4951 (0.0030)  &4.9273 (0.0043)  &5.5319 (0.0083)\\
19  &3.8694 (0.0055)  &4.1464 (0.0037)  &4.4755 (0.0039)  &4.8961 (0.0027)  &5.4838 (0.0031)\\
20  &3.8687 (0.0051)  &4.1364 (0.0041)  &4.4555 (0.0072)  &4.8673 (0.0042)  &5.4371 (0.0076)\\
21  &3.8672 (0.0064)  &4.1268 (0.0049)  &4.4401 (0.0052)  &4.8360 (0.0045)  &5.3927 (0.0027)\\
22  &3.8637 (0.0046)  &4.1215 (0.0037)  &4.4253 (0.0050)  &4.8136 (0.0043)  &5.3499 (0.0060)\\
23  &3.8610 (0.0032)  &4.1110 (0.0039)  &4.4093 (0.0057)  &4.7870 (0.0059)  &5.3118 (0.0056)\\
24  &3.8571 (0.0033)  &4.1015 (0.0051)  &4.3942 (0.0060)  &4.7650 (0.0026)  &5.2732 (0.0054)\\
25  &3.8541 (0.0054)  &4.0931 (0.0052)  &4.3803 (0.0032)  &4.7416 (0.0024)  &5.2453 (0.0045)
\end{tabular}

\caption{Cut off values}
\label{tab:var_cut_off_values}
\end{table}

>>>>

\section{Original Heteroskedastic Model of SAR data}
\label{sec:heteroskedastic_sar}

@@

\begin{equation}
\label{eqn:SAR Unit Amplitude PDF}
\caption{eqn:SAR Unit Amplitude PDF}
pdf(A_1) = 2A_1 e^{ - \left( A_1^2 \right) }
\end{equation}
\begin{equation}
  \label{eqn:SAR Unit Intensity PDF}
  \caption{eqn:SAR Unit Intensity PDF}
pdf(I_1) = e^{ \left( -I_1 \right) }
\end{equation}

@@

\begin{table}[!h]
\normalsize
\centering
\caption{ Mean and Variance of Original SAR data }
\label{tbl:orginal_sar_avg_var}
\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(A_1) = \frac{ \sqrt{\pi}}{2}$ & $var(A_1) = \frac{(4-\pi)}{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ & $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline 
\end{tabular}
\end{table}

@@

\section{The Effects of Heteroskedasticity in SAR Processing}%IVM: shortened to make it look nicer
\label{sec:heteroskedastic_sar_processing}

@@

%The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously.
As shown in the previous section,
  over heterogeneous area, the stochastic SAR speckle is heteroskedastic in nature.
Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
While the statistical model within individual resolution cells is well established,
  it is only applicable to homogeneous areas.
Practical images, however, are heterogeneous.
Furthermore, it is precisely this spatial variation that is often of high interest.
%And while the statistical model within individual resolution cells is well established,
%  the applicability of these models, however, are restricted to homogeneous areas. 
%Practical images, nevertheless, are heterogeneous. 
%Crucially it is this spatial variation that is of high interest. 
%This fact gives rise to the question that seemed obvious:
  %how to call an analysis area heterogeneous and subsequently
%  what to do in the case of heterogeneity.

@@

Heteroskedasticity also poses numerous challenges in designing an efficient estimator. Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator in serious doubt. 
If the variance is known \textit{a priori}, it has been proven \cite{Aitken_1934_ProcsRoyalSocEdinburg}, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most commonly known successful adaptive filters \cite{Lee_PAMI_1980, Kuan_1985_PAMI, Frost_PAMI_1982} do make use of weighted mean estimations. 
The problem, however, is that in SAR speckle filtering, variance is not known \textit{a priori}. 
And even though variance can be estimated from observable values, as the ambiguity circle goes, estimating the variance is as hard as estimating the underlying coefficient $\sigma$ itself.

@@

\section{The Homoskedastic Effect of Logarithmic Transformation}
\label{sec:homoskedastic_sar}

@@

\begin{equation}
  \label{eqn:SAR Unit Log Amplitude PDF}
  \caption{eqn:SAR Unit Log Amplitude PDF}
pdf(L_{1}^{A}) = 2 \cdot 2^{\left( 2 L_{1}^{A} \right)}e^{-2^{\left( 2 L_{1}^{A} \right) }} 
\end{equation}
\begin{equation}
  \label{eqn:SAR Log Amplitude PDF}
  \caption{eqn:SAR Log Amplitude PDF}
pdf(L_A) = 2 \cdot 2^{\left( 2 L_A - 2 \log_2 \sigma \right)}e^{-2^{\left( 2 L_A - 2 \log_2 \sigma \right)}} 
\end{equation}
\begin{equation}
pdf(L_{1}^{I}) = 2^{L_1^I} e^{-2^{L_1^I}}  
  \caption{eqn:SAR Unit Log Intensity PDF}
  \label{eqn:SAR Unit Log Intensity PDF}
\end{equation}
\begin{equation}
pdf(L_I) = 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
  \caption{eqn:SAR Log Intensity PDF}
  \label{eqn:SAR Log Intensity PDF}
\end{equation}

@@

\begin{table}[h]
\normalsize
\centering
\caption{ Mean and Variance of Log Transformed values: here the variance is no longer dependent on $\sigma$ }
\label{tbl:sar_log_domain_avg_var}
\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = - \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = - \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}
\end{table}

@@

\section{Consistent Measures of Distance in the Log-Transformed Domain}
\label{sec:consistent_measures_distance_sar}

@@

\begin{table}[H]
\centering
\caption{Cut off values}
\label{tab:var_cut_off_values}

\small
%awk -F"&" '{print $4}' tmp.0.txt | awk -F"(" '{print $1}'
\begin{tabular}{c|c|c|c|c|c}
No  & 70\%            &75\%             &80\%             &85\%             &90\%\\
\hline
2   &2.9024 (0.0252)  &3.7088 (0.0261)  &4.7960 (0.0327)  &6.3488 (0.0242)  &8.7974 (0.0370)\\
3   &3.4698 (0.0141)  &4.1308 (0.0177)  &4.9585 (0.0245)  &6.1176 (0.0136)  &7.9207 (0.0316)\\
4   &3.6505 (0.0225)  &4.2096 (0.0386)  &4.9392 (0.0347)  &5.9195 (0.0341)  &7.4209 (0.0162)\\
5   &3.7421 (0.0134)  &4.2513 (0.0165)  &4.8967 (0.0297)  &5.7729 (0.0170)  &7.0725 (0.0250)\\
6   &3.7850 (0.0149)  &4.2588 (0.0242)  &4.8611 (0.0160)  &5.6449 (0.0162)  &6.8062 (0.0282)\\
7   &3.8274 (0.0119)  &4.2686 (0.0102)  &4.8179 (0.0117)  &5.5447 (0.0114)  &6.6049 (0.0158)\\
8   &3.8468 (0.0110)  &4.2591 (0.0124)  &4.7747 (0.0176)  &5.4519 (0.0087)  &6.4370 (0.0085)\\
9   &3.8610 (0.0081)  &4.2503 (0.0125)  &4.7430 (0.0120)  &5.3688 (0.0085)  &6.2829 (0.0112)\\
10  &3.8663 (0.0089)  &4.2423 (0.0126)  &4.6967 (0.0102)  &5.3015 (0.0103)  &6.1574 (0.0116)\\
11  &3.8707 (0.0089)  &4.2284 (0.0109)  &4.6693 (0.0078)  &5.2387 (0.0111)  &6.0473 (0.0122)\\
12  &3.8763 (0.0063)  &4.2228 (0.0072)  &4.6370 (0.0139)  &5.1805 (0.0050)  &5.9502 (0.0044)\\
13  &3.8808 (0.0048)  &4.2089 (0.0083)  &4.6096 (0.0055)  &5.1315 (0.0092)  &5.8654 (0.0070)\\
14  &3.8761 (0.0048)  &4.1920 (0.0112)  &4.5816 (0.0069)  &5.0845 (0.0058)  &5.7870 (0.0106)\\
15  &3.8806 (0.0048)  &4.1901 (0.0063)  &4.5592 (0.0088)  &5.0372 (0.0076)  &5.7158 (0.0119)\\
16  &3.8774 (0.0032)  &4.1778 (0.0060)  &4.5397 (0.0049)  &4.9985 (0.0087)  &5.6483 (0.0083)\\
17  &3.8760 (0.0043)  &4.1682 (0.0035)  &4.5149 (0.0060)  &4.9652 (0.0051)  &5.5919 (0.0078)\\
18  &3.8708 (0.0083)  &4.1584 (0.0026)  &4.4951 (0.0030)  &4.9273 (0.0043)  &5.5319 (0.0083)\\
19  &3.8694 (0.0055)  &4.1464 (0.0037)  &4.4755 (0.0039)  &4.8961 (0.0027)  &5.4838 (0.0031)\\
20  &3.8687 (0.0051)  &4.1364 (0.0041)  &4.4555 (0.0072)  &4.8673 (0.0042)  &5.4371 (0.0076)\\
21  &3.8672 (0.0064)  &4.1268 (0.0049)  &4.4401 (0.0052)  &4.8360 (0.0045)  &5.3927 (0.0027)\\
22  &3.8637 (0.0046)  &4.1215 (0.0037)  &4.4253 (0.0050)  &4.8136 (0.0043)  &5.3499 (0.0060)\\
23  &3.8610 (0.0032)  &4.1110 (0.0039)  &4.4093 (0.0057)  &4.7870 (0.0059)  &5.3118 (0.0056)\\
24  &3.8571 (0.0033)  &4.1015 (0.0051)  &4.3942 (0.0060)  &4.7650 (0.0026)  &5.2732 (0.0054)\\
25  &3.8541 (0.0054)  &4.0931 (0.0052)  &4.3803 (0.0032)  &4.7416 (0.0024)  &5.2453 (0.0045)
\end{tabular}

\end{table}

### 2014-06-26 4/polsar.tex
auto

This chapter derives several scalar statistical models for the
                determinant of the POLSAR covariance matrix and
                show that they are heteroskedastic in their original
                domain as well as homoskedastic in the log-transformed
                domain.
It
                also derives a heteroskedastic discrimination measures
                 as well as several homoskedastic measures of
                distance for the data.
Subsequently the statistical models for SAR are shown to be a special case of
                the proposed models for POLSAR
And finally these proposed models are validated against real-life practical data.
Mathematical derivations of the proposed models are presented in the Appendix. %***IVM: should say "Appendix A" or whatever it is?
%The last section of this chapter details the mathematical derivations of these proposed models,
%  which may only be helpful for mathematically inclined readers.

@@

@@

@@

This section introduces the consistent sense of distance from a few different perspectives.
First assuming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
the following random variables,
  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are observables according to their definitions:

@@

From another perspective where the POLSAR is known as having come from an homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
%\begin{eqnarray}
%\end{eqnarray}
\begin{equation}
 \label{eqn:dispersion_observable}
 \caption{eqn:POLSAR Dispersion Observable}
 \mathbb{D} = \ln{|C_v|} - avg(\ln{|C_v|})  
\end{equation}
\begin{equation}
  \label{eqn:contrast_observable}
  \caption{eqn:POLSAR Contrast Observable}
  \mathbb{C} = \ln(|C_{v1}|) - \ln(|C_{v2}|)
\end{equation}

@@

This newly derived model for multi-look SAR data can also be validated against real-life data.
Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
In the experiment, the intensity of a single-channel of SAR data (HH) for an homogeneous area in the AIRSAR Flevoland dataset is extracted.%***IVM do you need to give a ref to the dataset?
Then the histograms for the log-distance and and contrast are plotted against the theoretical PDF given above.
The ENL is set to the nominal number of 4.
A good visual match is apparent in the final plotted results.

@@

This section describes the test to validate the proposed models  against real-life captured data. The validation procedure is as follows. Using the stochastic
models  derived in the previous sections, 
histogram plots of its simulated data are generated graphically. This is then compared against  the histogram plots of the  real-life captured data samples extracted from an homogeneous area.

As such,  the theoretical models can be validated if, for the
same parameters, the two plots match each other reasonably well.
For this verification, an homogeneous area was chosen from the AIRSAR Flevoland POLSAR data. Theoretical models are then verified against the  real life data. The validations include the following models: the determinant and
its log-transformed models, together with the various dissimilarity measures, namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.

@@

Apart from dispersion and contrast,
the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
There are two ways to estimate this quantity over an homogeneous area.
The traditional way is to simply assume that the true signal is equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
Both approaches will be explored in this section.
However, given that the log-determinant average has already been computed earlier, 
  the second approach is used first for the validation of determinant-ratio and log-distance.

@@

\subsection{Estimating the Effect Number-of-Looks (ENL)}

@@

This approach was also used in \cite{Anfinsen_2009_TGRS_3795}, where the same equation 
  as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
Instead of relying on the equations for statistical mean to find ENL,
  the approach here makes use of the variance statistics in the homoskedastic log-domain to find ENL.
Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
\begin{equation*}
  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
\end{equation*}
where $\psi^1()$ denotes tri-gamma function.

@@

For this test a sample RADARSAT2 dataset is used. 
The dataset is in its Fine-Quad mode Single-Look format,
  and nine-look processing is applied.
The dispersion histogram in the log-transformed domain is computed over an homogeneous area.
The histograms generated by the theoretical models for  nominal ENL value
  of 9 are then plotted %for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted
in Fig. \ref{fig:handling_radarsat2_oversampling_practice}. The nine-look histogram is the narrower and higher curve.
As can be seen, the match is not very good between this and the observed data, displayed as points.

@@

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling consequences in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling consequences in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{9-look processed Radarsat2 data does not exactly exhibit 9-look data characteristics. An homoskedastic model in the log-transformed domain can be used to successfully estimate the effective ENL and thus offer a better model of the data.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}

>>>>

This chapter derives several scalar statistical models for the
                determinant of the POLSAR covariance matrix and
                show that they are heteroskedastic in their original
                domain as well as homoskedastic in the log-transformed
                domain.
It
                also derives a heteroskedastic discrimination measures
                 as well as several homoskedastic measures of
                distance for the data.
Subsequently the statistical models for SAR are shown to be a special case of
                the proposed models for POLSAR. 
And finally these proposed models are validated against real-life practical data.
Mathematical derivations of the proposed models are presented in the Appendix. %***IVM: should say "Appendix A" or whatever it is?
%The last section of this chapter details the mathematical derivations of these proposed models,
%  which may only be helpful for mathematically inclined readers.

@@

\subsection{The Determinant and Log-Determinant Models}

@@

\subsection{The Statistical Properties of the Proposed Models}

@@

This section introduces the consistent sense of distance from a few different perspectives.

\subsection{The Determinant-Ratio and Log-Distance Models}

First assuming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
the following random variables,
  namely determinat-ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are observables according to their definitions:

@@

\subsection{The Dispersion and Contrast Models}

From another perspective where the POLSAR is known as having come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
%\begin{eqnarray}
%\end{eqnarray}
\begin{equation}
 \label{eqn:dispersion_observable}
 \caption{eqn:POLSAR Dispersion Observable}
 \mathbb{D} = \ln{|C_v|} - avg(\ln{|C_v|})  
\end{equation}
\begin{equation}
  \label{eqn:contrast_observable}
  \caption{eqn:POLSAR Contrast Observable}
  \mathbb{C} = \ln(|C_{v1}|) - \ln(|C_{v2}|)
\end{equation}

\subsection{The Statistical Properties of the Proposed Models}

@@

This newly derived model for multi-look SAR data can also be validated against real-life data.
Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
In the experiment, the intensity of a single-channel of SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.%***IVM do you need to give a ref to the dataset?
Then the histograms for the log-distance and and contrast are plotted against the theoretical PDF given above.
The ENL is set to the nominal number of 4.
A good visual match is apparent in the final plotted results.

@@

This section describes the test to validate the proposed models  against real-life captured data. The validation procedure is as follows. Using the stochastic
models  derived in the previous sections, 
histogram plots of its simulated data are generated graphically. This is then compared against  the histogram plots of the  real-life captured data samples extracted from a homogeneous area.

As such,  the theoretical models can be validated if, for the
same parameters, the two plots match each other reasonably well.
For this verification, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data. Theoretical models are then verified against the  real life data. The validations include the following models: the determinant and
its log-transformed models, together with the various dissimilarity measures, namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.

@@

Apart from dispersion and contrast,
the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
There are two ways to estimate this quantity over a homogeneous area.
The traditional way is to simply assume that the true signal is equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
Both approaches will be explored in this section.
However, given that the log-determinant average has already been computed earlier, 
  the second approach is used first for the validation of determinant-ratio and log-distance.

@@

\subsection{Estimating the Effective Number-of-Looks (ENL)}

@@

This approach was also used in \cite{Anfinsen_2009_TGRS_3795}, where the same equation 
  as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
Instead of relying on the equations for statistical mean to find ENL,
  the approach here makes use of the variance statistics in the homoskedastic log-domain to find ENL.
Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
\begin{equation}
  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
\end{equation}
where $\psi^1()$ denotes tri-gamma function.

@@

For this test a sample RADARSAT2 dataset is used. 
The dataset is in its Fine-Quad mode Single-Look format,
  and nine-look processing is applied.
The dispersion histogram in the log-transformed domain is computed over a homogeneous area.
The histograms generated by the theoretical models for  nominal ENL value
  of 9 are then plotted %for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted
in Fig. \ref{fig:handling_radarsat2_oversampling_practice}. The nine-look histogram is the narrower and higher curve.
As can be seen, the match is not very good between this and the observed data, displayed as points.

@@

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling consequences in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling consequences in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{9-look processed Radarsat2 data does not exactly exhibit 9-look data characteristics. A homoskedastic model in the log-transformed domain can be used to successfully estimate the effective ENL and thus offer a better model of the data.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}
